---
site: blogdown:::blogdown_site
---

# Analysis of movies based on IMDB dataset

```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```

```{r load-libraries, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
library(rvest)    # scrape websites
library(purrr)  
library(lubridate) #to handle dates
library(ggrepel)
```

I'm a big fan watching movies. In this project, I will look at a subset sample of movies, taken from the Kaggle IMDB 5000 movie dataset. I would like to explore what factors influence the gross return of a movie. 


```{r,load_movies, warning=FALSE, message=FALSE}

movies <- read_csv(here::here("data", "movies.csv"))
glimpse(movies)

```
The table below shows how many movies there are in each genre in my data set. 

```{R,movies_by_genre}
#Produce a table with the count of movies by genre, ranked in descending order

movies %>% 
  group_by(genre) %>% 
  summarise(n=n()) %>% 
  arrange(desc(n))

```

First, I will examine the relationship between the gross return of movies and their facebook likes.
  
```{r, gross_on_fblikes}
ggplot(
  data=movies,
  mapping=aes(
    x=cast_facebook_likes,
    y=gross))+
    geom_point()+
  scale_x_log10()+
  geom_smooth()

```
As illustrated by the plot, the number of facebook likes that the cast has received is not likely to be a good predictor of how much money a movie will make at the box office but it can be a good indicator when the number of likes reaches a certain level. 


Then, I will examine the relationship between the gross return of movies and and their budget. 

```{r, gross_on_budget}
ggplot(
  data=movies,
  mapping=aes(
    x=budget,
    y=gross))+
    geom_point()+
  geom_smooth()
```

I find that the budget is likely to be a good indicator of how much money a movie will make at the box office. 
  
  
I produce a similar plot for IMDB ratings. 

```{r, gross_on_rating}
gross_rating_scatterplot<-
  ggplot(
    data=movies,
    mapping=aes(
      x=rating,
      y=gross,
      color=genre))+
    geom_point()+
  scale_y_log10()

gross_rating_scatterplot+
  facet_wrap(~genre)
```

According to this plot, IMDB ratings are likely to be a good predictor of how much money a movie will make at the box office for certain genres such as action and comedy but it is difficult to make assumptions for some genres such as thriller, musical and romance due to lack of data.
 

