---
site: blogdown:::blogdown_site
---

# Analysis of movies- IMDB dataset

```{r load-libraries, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
library(rvest)    # scrape websites
library(purrr)  
library(lubridate) #to handle dates
library(ggrepel)
```



```{r,load_movies, warning=FALSE, message=FALSE}

movies <- read_csv(here::here("data", "movies.csv"))
glimpse(movies)

```

```{R,movies_by_genre}
#Produce a table with the count of movies by genre, ranked in descending order

movies %>% 
  group_by(genre) %>% 
  summarise(n=n()) %>% 
  arrange(desc(n))

```
- Produce a table with the average gross earning and budget (`gross` and `budget`) by genre. Calculate a variable `return_on_budget` which shows how many $ did a movie make at the box office for each $ of its budget. Ranked genres by this `return_on_budget` in descending order
```{R,movies_average}
movies %>% 
  group_by(genre) %>% 
  summarise(avg_gross=mean(gross),
            avg_budget=mean(budget))

```
```{R,return_on_budget}
movies_ret <- movies %>% 
  group_by(genre) %>% 
  summarise(avg_gross=mean(gross),
            avg_budget=mean(budget)) %>% 
  mutate(return_on_budget=avg_gross/avg_budget) %>% 
  arrange(desc(return_on_budget))

movies_ret

```

- Produce a table that shows the top 15 directors who have created the highest gross revenue in the box office. Don't just show the total gross amount, but also the mean, median, and standard deviation per director.
```{R,movies_directors}
directors_top15 <- movies %>% 
  group_by(director) %>% 
  summarise(total_gross=sum(gross),
            mean_gross=mean(gross),
            median_gross=median(gross),
            stdev_gross=sd(gross)) %>% 
  arrange(desc(total_gross)) %>% 
  head(15)

directors_top15

```

- Finally, ratings. Produce a table that describes how ratings are distributed by genre. We don't want just the mean, but also, min, max, median, SD and some kind of a histogram or density graph that visually shows how ratings are distributed.
```{R,movies_rating}

movies_rating_table<-movies %>% 
  group_by(genre) %>% 
  summarise(mean_rating=mean(rating),
            min_rating=min(rating),
            max_rating=max(rating),
            median_rating=median(rating),
            stdev_rating=STDEV(rating)) 

movies_rating_table

ggplot(
  data=movies_rating_table,
  mapping=aes(
    x=mean_rating))+
  geom_density()

ggplot(
  data=movies_rating_table,
  mapping=aes(
    x=min_rating))+
  geom_density()
 
ggplot(
  data=movies_rating_table,
  mapping=aes(
    x=max_rating))+
  geom_density()

ggplot(
  data=movies_rating_table,
  mapping=aes(
    x=median_rating))+
  geom_density()

ggplot(
  data=movies_rating_table,
  mapping=aes(
    x=stdev_rating))+
  geom_density()
```

## Use `ggplot` to answer the following

  - Examine the relationship between `gross` and `cast_facebook_likes`. Produce a scatterplot and write one sentence discussing whether the number of facebook likes that the cast has received is likely to be a good predictor of how much money a movie will make at the box office. What variable are you going to map to the Y- and X- axes?
  
  
```{r, gross_on_fblikes}
ggplot(
  data=movies,
  mapping=aes(
    x=cast_facebook_likes,
    y=gross))+
    geom_point()+
  scale_x_log10()+
  geom_smooth()

```
The number of facebook likes that the cast has received is not likely to be a good predictor of how much money a movie will make at the box office but it can be a good indicator when the number of likes reaches a certain level. 


  - Examine the relationship between `gross` and `budget`. Produce a scatterplot and write one sentence discussing whether budget is likely to be a good predictor of how much money a movie will make at the box office.

```{r, gross_on_budget}
ggplot(
  data=movies,
  mapping=aes(
    x=budget,
    y=gross))+
    geom_point()+
  geom_smooth()
```
The budget is likely to be a good indicator of how much money a movie will make at the box office. 
  
  
  - Examine the relationship between `gross` and `rating`. Produce a scatterplot, faceted by `genre` and discuss whether IMDB ratings are likely to be a good predictor of how much money a movie will make at the box office. Is there anything strange in this dataset?

```{r, gross_on_rating}
gross_rating_scatterplot<-
  ggplot(
    data=movies,
    mapping=aes(
      x=rating,
      y=gross,
      color=genre))+
    geom_point()+
  scale_y_log10()

gross_rating_scatterplot+
  facet_wrap(~genre)
```
IMDB ratings are likely to be a good predictor of how much money a movie will make at the box office for certain genres such as action and comedy but it is difficult to make assumptions for some genres such as thriller, musical and romance due to lack of data.
One strange thing about this plot is that in some charts there are multiple levels of gross for a given level of rating. 

